Predicting instabilities of a tuneable ring laser with an iterative map model

### 2021-05-29 Papers/Journal/Cavity.tex
Finished Chris edits
Updated Figure 1

\begin{tikzpicture}
% Two laser loops
\draw [rounded corners=4mm] (0,0) rectangle ++(6,4);
\draw [rounded corners=4mm] (0,0) rectangle ++(-1.5,4);

% Gain
\draw (0.5,2.25) circle (0.5cm);
\draw (0.5,2) circle (0.5cm) node [anchor=west,xshift=0.5cm,align=center] {Er-doped \\ fibre};
\draw (0.5,1.75) circle (0.5cm);

% Modulator and pump
\filldraw[fill=white, draw=black] (2,-0.75) rectangle ++(2,1.5) node [midway] {Modulator};
\filldraw[fill=white, draw=black] (-2.1,1.5) rectangle ++(1.2,1) node [midway] {Pump};

@@

% Circulators
\filldraw[fill=white, draw=black] (6,2) circle (0.5cm);
\draw[->,>=stealth] (6,2.325) arc (90:360:0.325cm);

\filldraw[fill=white, draw=black] (0,0) circle (0.5cm);
\draw[->,>=stealth] (0,0.325) arc (90:360:0.325cm);

\filldraw[fill=white, draw=black] (0,4) circle (0.5cm) node [anchor=south,align=center,yshift=0.5cm] {Optical circulator};
\draw[->,>=stealth] (0,4.325) arc (90:360:0.325cm);

% Arrows
\draw [->,>=stealth,domain=20:70,blue] plot ({0.675*cos(\x)}, {0.675*sin(\x)});
\draw [->,>=stealth,domain=110:160,red] plot ({0.675*cos(\x)}, {0.675*sin(\x)});
\draw [->,>=stealth,domain=110:160,blue] plot ({6+0.675*cos(\x)}, {2+0.675*sin(\x)});
\draw [->,>=stealth,domain=200:250,blue] plot ({6+0.675*cos(\x)}, {2+0.675*sin(\x)});
\draw [->,>=stealth,domain=200:250,red] plot ({0.675*cos(\x)}, {4+0.675*sin(\x)});
\draw [->,>=stealth,domain=290:340,blue] plot ({0.675*cos(\x)}, {4+0.675*sin(\x)});

>>>>

\begin{tikzpicture}
% Two laser loops
\draw [rounded corners=4mm] (0,0) rectangle ++(-1,4); % Pump
\draw [fill=white, white] (0, -0.1) rectangle ++(-1.1,2); % Hide pump
\draw [rounded corners=4mm] (0,0) rectangle ++(6,4); % Main

% Isolator
\filldraw[fill=white, draw=black] (1,-0.25) rectangle ++(1,0.5) node [midway, anchor=north, yshift=-6] {Isolator};
\draw[-triangle 90] (1.9,0) -- (1.1,0);
\draw[very thick] (1.9,0) -- (1.2,0);

% Gain
\draw (0.5,2.25) circle (0.5cm);
\draw (0.5,2) circle (0.5cm) node [anchor=west,xshift=0.5cm,align=center] {Er-doped \\ gain fibre};
\draw (0.5,1.75) circle (0.5cm);

% Modulator and pump
\filldraw[fill=white, draw=black] (3,-0.75) rectangle ++(2,1.5) node [midway] {Modulator};
\filldraw[fill=white, draw=black] (-1.6,1.5) rectangle ++(1.2,1) node [midway] {Pump};

@@

% Circulators
\filldraw[fill=white, draw=black] (6,2) circle (0.5cm) node [anchor=west,align=center,xshift=0.5cm] {OC};
\draw[->,>=stealth] (6,2.325) arc (90:360:0.325cm);

% \filldraw[fill=white, draw=black] (0,0) circle (0.5cm);
% \draw[->,>=stealth] (0,0.325) arc (90:360:0.325cm);

% \filldraw[fill=white, draw=black] (0,4) circle (0.5cm);
% \draw[->,>=stealth] (0,4.325) arc (90:360:0.325cm);

% WDMs
\filldraw[fill=white, draw=black] (-0.15,3.8) rectangle ++(0.3,-0.6) node [midway, anchor=west, xshift=3] {WDM};
% \filldraw[fill=white, draw=black] (-0.15,0.2) rectangle ++(0.3,0.6) node [midway, anchor=west, xshift=2] {WDM};

% Arrows
% \draw [->,>=stealth,domain=20:70,blue] plot ({0.675*cos(\x)}, {0.675*sin(\x)});
% \draw [->,>=stealth,domain=110:160,red] plot ({0.675*cos(\x)}, {0.675*sin(\x)});
\draw [->,>=stealth,domain=110:160,blue] plot ({6+0.675*cos(\x)}, {2+0.675*sin(\x)});
\draw [->,>=stealth,domain=200:250,blue] plot ({6+0.675*cos(\x)}, {2+0.675*sin(\x)});
% \draw [->,>=stealth,domain=200:250,red] plot ({0.675*cos(\x)}, {4+0.675*sin(\x)});
% \draw [->,>=stealth,domain=290:340,blue] plot ({0.675*cos(\x)}, {4+0.675*sin(\x)});

### 2021-05-29 Papers/Journal/Tuneable_Lasers.tex
Updated Figure 1

\usetikzlibrary{patterns,decorations.pathreplacing}
\usetikzlibrary{arrows.meta}
\usetikzlibrary{shapes.arrows, fadings}

@@

\begin{figure}[tbp]
	\centering
	\input{Cavity}
	\caption{Common cavity construction of a fibre ring laser~\cite{burgoyne2014, chung2017, lapre2019, shao2019}. The pump laser travels clockwise around the left-hand loop (red arrows) energizing the Er-doped gain fibre. The main laser travels clockwise around the right-hand loop (blue arrows), with most of the pulse exiting the cavity through the optical coupler.}
	\label{fig:cavity}
\end{figure}

>>>>

\usetikzlibrary{patterns,decorations.pathreplacing}
\usetikzlibrary{arrows.meta}
\usetikzlibrary{shapes.arrows, fadings}
\usetikzlibrary{arrows}
\usetikzlibrary{decorations.markings}

@@

\begin{figure}[tbp]
	\centering
	\input{Cavity}
	\caption{Common cavity construction of a fibre ring laser~\cite{burgoyne2014, chung2017, lapre2019, shao2019}. The laser travels clockwise around the loop, with most of the pulse exiting the cavity through the optical coupler. CFBG, chirped fibre Bragg grating; OC, optical circulator; WDM, wavelength division multiplexer}
	\label{fig:cavity}
\end{figure}
